New lower bounds for Schur and weak Schur numbers

### 2021-04-14 article/appendix.tex
commande \WS

This template provides the inequality \(WS(n+3) \geqslant 42S(n) + 24\)
by placing one last number, here represented by \(\mathbf{(N+1)}\), in the first subset.

>>>>

This template provides the inequality \(\WS (n+3) \geqslant 42S(n) + 24\)
by placing one last number, here represented by \(\mathbf{(N+1)}\), in the first subset.

### 2021-04-14 article/article.tex
commande \WS

\usepackage[table]{xcolor}

@@

\usepackage[a4paper, total={6in, 8in}]{geometry}

@@

This article provides new lower bounds for both Schur and weak Schur numbers. These results were obtained by continuing on
Rowley's "templates"-based approach for Ramsey and Schur numbers. Finding suitable templates allows us to apply Rowley's construction
to get explicit partitions improving lower bounds as well as the growth rate of both Schur numbers and Ramsey numbers \(R_n(3)\). 
We also developed a new method to improve lower bounds on weak Schur numbers. Furthermore, this paper tries to analyze former 
works on the subject based on the principle that good partitions into \(n+1\) subsets start with good partitions 
into \(n\) subsets. We show that exceeding the previous lower bound \(WS(6) \geqslant 582\) is impossible with such an assumption upon 
imposing certain conditions on the good 5-subsets partition. The new lower bounds include \(S(9) \geqslant 17803\), \(S(10) \geqslant 60948\), 
\(WS(9) \geqslant 22536 \) and \(WS(10) \geqslant 71214 \).

@@

\par
These new results come from an extension of Rowley's template-based approach for Ramsey graphs and Schur numbers which is relatively new. 
Therefore, we would not be surprised if lower bounds are later improved using better templates. Moreover, studying specifically \(S^+(n)\) and 
\(WS^+(n)\) might be of interest as they are closely related to Schur and weak Schur numbers.

>>>>

\usepackage[table]{xcolor}
\usepackage[a4paper, total={6in, 8in}]{geometry}

@@

\newcommand{\WS}{\mathit{WS}}

@@

This article provides new lower bounds for both Schur and weak Schur numbers. These results were obtained by continuing on
Rowley's "templates"-based approach for Ramsey and Schur numbers. Finding suitable templates allows us to apply Rowley's construction
to get explicit partitions improving lower bounds as well as the growth rate of both Schur numbers and Ramsey numbers \(R_n(3)\).
We also developed a new method to improve lower bounds on weak Schur numbers. Furthermore, this paper tries to analyze former
works on the subject based on the principle that good partitions into \(n+1\) subsets start with good partitions
into \(n\) subsets. We show that exceeding the previous lower bound \(\WS (6) \geqslant 582\) is impossible with such an assumption upon
imposing certain conditions on the good 5-subsets partition. The new lower bounds include \(S(9) \geqslant 17803\), \(S(10) \geqslant 60948\),
\(\WS (9) \geqslant 22536 \) and \(\WS (10) \geqslant 71214 \).

@@

\par
These new results come from an extension of Rowley's template-based approach for Ramsey graphs and Schur numbers which is relatively new.
Therefore, we would not be surprised if lower bounds are later improved using better templates. Moreover, studying specifically \(S^+(n)\) and
\(\WS^+(n)\) might be of interest as they are closely related to Schur and weak Schur numbers.

### 2021-04-14 article/definitions_notations.tex
modification organisation generale
commande \WS

\section{Introduction, context and notations}

@@

\begin{definition}
Let \(n \in \mathbb{N}^*\). There exists a greatest integer that we denote \(S(n)\) (\textit{resp. \(WS(n)\)}) such that
\([\![1,S(n)]\!]\) (resp. \([\![1,WS(n)]\!]\)) can be partitioned into \(n\) sum-free subsets (resp. weakly sum-free
subsets). \(S(n)\) is called the \textit{\(n\)\textsuperscript{th} Schur number} and \textit{\(WS(n)\) the
\(n\)\textsuperscript{th} weak
Schur number}.
\end{definition}

>>>>

\section{Definitions and notations}

@@

\begin{definition}
Let \(n \in \mathbb{N}^*\). There exists a greatest integer that we denote \(S(n)\) (\textit{resp. \(\WS (n)\)}) such that
\([\![1,S(n)]\!]\) (resp. \([\![1, \WS (n)]\!]\)) can be partitioned into \(n\) sum-free subsets (resp. weakly sum-free
subsets). \(S(n)\) is called the \textit{\(n\)\textsuperscript{th} Schur number} and \textit{\(\WS (n)\) the
\(n\)\textsuperscript{th} weak
Schur number}.
\end{definition}

### 2021-04-14 article/sat.tex
commande \WS

In this section, we first reframe the question of the existence of (weakly) sum-free partitions as a boolean
satisfiability (SAT) problem. We then provide evidence which indicates that the main assumption made by papers which
found the previous best known lower bounds for weak Schur numbers may not be correct. Finally, we obtain stronger
results than those previously known for \(WS(5)\) while gaining several orders of magnitude in computation time by
giving additional information to the SAT solver without losing in generality. In this section, we assume that the
subsets are ordered.

@@

In the above formula, every color plays a symmetric role. Hence the search space can reduced by \(k!\) by ordering the
subsets, that is by
enforcing that \(m_1 < ... < m_k\). The corresponding clauses are: \linebreak
\textbf{symmetry breaking:} \(x^{(1)}_1 = 1\) and \(\forall c \in [\![2,k-1]\!], \forall i \in [\![1,WS(c - 1)+1]\!],
x^{(1)}_c \lor ... \lor x^{(i)}_c \lor \neg x^{(i+1)}_{c+1}\)

@@

\subsection{The search space previously used in computer search for lower bounds may not contain the optimal partitions}
Rowley's new lower bound for \(WS(6)\) (642) \cite{RowleyWS} was a quite significant improvement upon
the former
best known lower bound (582) \cite{EliahouBook}. This previous lower bound was found using a computer
(often with Monte-Carlo methods) and by making the
assumption that a good partition for \(WS(n+1)\) starts with a good partition for \(WS(n)\) which is true for small
values of \(n\).
Therefore, one may wonder whether the limiting factor are the assumptions or the methods used to search for partitions.
It appears that the search space
induced by these assumptions does not contain the optimal partitions.

@@

\par
The above theorem shows that the previous lower bound for \(WS(6)\) is optimal in the search space considered by the
papers which found it.
Therefore, finding a partition of \([\![1,n]\!]\) in 6 weakly sum-free subsets for some \(n \geqslant 590\) which does
not have a template-like structure
would be extremely interesting since it could give indications on a new search space for improving lower bounds with a
computer. More generally,
it questions the search space previously used for finding lower bounds for \(WS(n)\) with a computer. In particular, to
our knowledge every paper
that found the lower bound \(WS(5) \geqslant 196\) used this assumption. Therefore one may wonder
if this actually a good lower
bound. In the next subsection, we give properties that a partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets has
to verify.

\subsection{Weak Schur number five}
As explained in the previous subsection, the search space used for showing that \(WS(5) \geqslant 196\) may not contain
optimal solution. In this subsection,
we give necessary conditions for a hypothetical partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets using the
same type of methods as in the
previous subsection.

\begin{notation}
Let \(P\) be a predicate over weakly sum-free partitions. We denote by \(WS(n | P)\) the greatest number \(p\) such that
there exists a partition of
\([\![1,p]\!]\) in n weakly sum-free subsets which verifies P.
\end{notation}

\par
\cite{ELIAHOU2012175} verified with a SAT solver that there are no partition in 5 weakly sum-free subsets of
\([\![1,197]\!]\) with
\(A_5 = \{67, 68\} \cup [\![70,134]\!] \cup \{136\}\) in 17 hours and could not provide a similar result when only
assuming \(m_5 = 67\) even after several
weeks of runtime. By using the same method as above, we were able to verify that \(WS(5 | m_5 = 67) = 196\) in 0.5
seconds with the SAT solver glucose \cite{Glucose}
on a 2.60 GHz Intel i7 processor PC (we used the non-parallel version here for the sake of comparison but in the rest of
this subsection, we used the parallel version of glucose).
The additional information we gave to the SAT solver is that every partition of \([\![1,66]\!]\) in 4 weakly sum-free
subsets starts with a partition of
\([\![1,23]\!]\) in 3 weakly sum-free subsets (this can be checked in a few dozens of minutes with a SAT solver). Among
the 3 partitions of \([\![1,23]\!]\) in
3 weakly sum-free subsets, every number always appears in the same subset except for 16 and 17 which can appear in two
different subsets. We hardcoded
this external knowledge in the propositional formula which allowed us to gain several orders of magnitude in computation
time. Since \(WS(4) = 66\), we have \(m_5 \leqslant 67\). We give the stronger following result.

@@

More precisely, we verified the following results (\(max~m_5\) is the greatest value of \(m_5\) for which we have not
verified that \(WS(5 | m_5) \leq 196\)).

@@

\begin{center}
\begin{tabular}{| c | *{21}{c |}}
	\hline
	\(m_4\) & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 & 13 & 14 & 15 & 16 & 17 & 18 & 19 & 20 & 21 & 22 & 23 & 24 \\
	\hline
	\(WS(4 | m_4) + 1\) & 55 & 59 & 60 & 59 & 59 & 60 & 60 & 60 & 60 & 64 & 63 & 64 & 61 & 64 & 63 & 65 & 65 & 65 & 65 & 66
	& 67 \\
	\hline
	\(max~m_5\) & 49 & 51 & 54 & 53 & 54 & 54 & 55 & 55 & 55 & 55 & 55 & 56 & 57 & 57 & 59 & 59 & 59 & 59 & 59 & 58 & 53 \\
	\hline
\end{tabular}
\end{center}

>>>>

In this section, we first reframe the question of the existence of (weakly) sum-free partitions as a boolean
satisfiability (SAT) problem. We then provide evidence which indicates that the main assumption made by papers which
found the previous best known lower bounds for weak Schur numbers may not be correct. Finally, we obtain stronger
results than those previously known for \(\WS (5)\) while gaining several orders of magnitude in computation time by
giving additional information to the SAT solver without losing in generality. In this section, we assume that the
subsets are ordered.

@@

In the above formula, every color plays a symmetric role. Hence the search space can reduced by \(k!\) by ordering the
subsets, that is by
enforcing that \(m_1 < ... < m_k\). The corresponding clauses are: \linebreak
\textbf{symmetry breaking:} \(x^{(1)}_1 = 1\) and \(\forall c \in [\![2,k-1]\!], \forall i \in [\![1, \WS (c - 1)+1]\!],
x^{(1)}_c \lor ... \lor x^{(i)}_c \lor \neg x^{(i+1)}_{c+1}\)

@@

\subsection{The search space previously used in computer search for lower bounds may not contain the optimal partitions}
Rowley's new lower bound for \(\WS (6)\) (642) \cite{RowleyWS} was a quite significant improvement upon
the former
best known lower bound (582) \cite{EliahouBook}. This previous lower bound was found using a computer
(often with Monte-Carlo methods) and by making the
assumption that a good partition for \(\WS (n+1)\) starts with a good partition for \(\WS (n)\) which is true for small
values of \(n\).
Therefore, one may wonder whether the limiting factor are the assumptions or the methods used to search for partitions.
It appears that the search space
induced by these assumptions does not contain the optimal partitions.

@@

\par
The above theorem shows that the previous lower bound for \(\WS (6)\) is optimal in the search space considered by the
papers which found it.
Therefore, finding a partition of \([\![1,n]\!]\) in 6 weakly sum-free subsets for some \(n \geqslant 590\) which does
not have a template-like structure
would be extremely interesting since it could give indications on a new search space for improving lower bounds with a
computer. More generally,
it questions the search space previously used for finding lower bounds for \(\WS (n)\) with a computer. In particular, to
our knowledge every paper
that found the lower bound \(\WS (5) \geqslant 196\) used this assumption. Therefore one may wonder
if this actually a good lower
bound. In the next subsection, we give properties that a partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets has
to verify.

\subsection{Weak Schur number five}
As explained in the previous subsection, the search space used for showing that \(\WS (5) \geqslant 196\) may not contain
optimal solution. In this subsection,
we give necessary conditions for a hypothetical partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets using the
same type of methods as in the
previous subsection.

\begin{notation}
Let \(P\) be a predicate over weakly sum-free partitions. We denote by \(\WS (n | P)\) the greatest number \(p\) such that
there exists a partition of
\([\![1,p]\!]\) in n weakly sum-free subsets which verifies P.
\end{notation}

\par
\cite{ELIAHOU2012175} verified with a SAT solver that there are no partition in 5 weakly sum-free subsets of
\([\![1,197]\!]\) with
\(A_5 = \{67, 68\} \cup [\![70,134]\!] \cup \{136\}\) in 17 hours and could not provide a similar result when only
assuming \(m_5 = 67\) even after several
weeks of runtime. By using the same method as above, we were able to verify that \(\WS (5 | m_5 = 67) = 196\) in 0.5
seconds with the SAT solver glucose \cite{Glucose}
on a 2.60 GHz Intel i7 processor PC (we used the non-parallel version here for the sake of comparison but in the rest of
this subsection, we used the parallel version of glucose).
The additional information we gave to the SAT solver is that every partition of \([\![1,66]\!]\) in 4 weakly sum-free
subsets starts with a partition of
\([\![1,23]\!]\) in 3 weakly sum-free subsets (this can be checked in a few dozens of minutes with a SAT solver). Among
the 3 partitions of \([\![1,23]\!]\) in
3 weakly sum-free subsets, every number always appears in the same subset except for 16 and 17 which can appear in two
different subsets. We hardcoded
this external knowledge in the propositional formula which allowed us to gain several orders of magnitude in computation
time. Since \(\WS (4) = 66\), we have \(m_5 \leqslant 67\). We give the stronger following result.

@@

More precisely, we verified the following results (\(max~m_5\) is the greatest value of \(m_5\) for which we have not
verified that \(\WS (5 | m_5) \leq 196\)).

@@

\begin{center}
\begin{tabular}{| c | *{21}{c |}}
	\hline
	\(m_4\) & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 & 13 & 14 & 15 & 16 & 17 & 18 & 19 & 20 & 21 & 22 & 23 & 24 \\
	\hline
	\(\WS (4 | m_4) + 1\) & 55 & 59 & 60 & 59 & 59 & 60 & 60 & 60 & 60 & 64 & 63 & 64 & 61 & 64 & 63 & 65 & 65 & 65 & 65 & 66
	& 67 \\
	\hline
	\(max~m_5\) & 49 & 51 & 54 & 53 & 54 & 54 & 55 & 55 & 55 & 55 & 55 & 56 & 57 & 57 & 59 & 59 & 59 & 59 & 59 & 58 & 53 \\
	\hline
\end{tabular}
\end{center}

### 2021-04-14 article/weakschur.tex
commande \WS

In this section, we generalize Rowley's constructions in \cite{RowleyWS}. We then introduce, by analogy with the third
section, the
integer \(WS^+(n)\)
to build suitable templates.

@@

Up to now, there was no equivalent for weak Schur numbers of Abott and Hanson's construction \cite{AbbottHanson}. Here
we
give a general lower bound for weak Schur numbers as a function of both regular and weak Schur numbers.
The following theorem, inspired by Rowley's inequalities for \(WS(n+1)\) and \(WS(n+2)\), was found and proved
by Romain Ageron.

@@

In particular, if we choose \(q = WS(n)\) and \(p = S(k)\) in the last theorem, the next corollary follows.

\begin{corollary}
\( \forall (n,k) \in (\mathbb{N}^*)^2 \text{, } WS(n+k) \geqslant S(k) \left (WS(n) + \left \lceil \frac{WS(n)}{2}
\right \rceil +1 \right) + WS(n)\)
\end{corollary}

@@

\begin{remark}
In the above ineqality, a "\(+1\)" can be added to the lower bound if \(WS(n)\) is odd (more generally if \(q\) is odd in the theorem). However, it makes the proof less
clear and it is never useful in practice.
\end{remark}

@@

\begin{remark}
This formula includes the results of Rowley \cite{RowleyWS} as a special case. For \(n>2\),
this formula does not give new lower bounds but in the same way as we introduced \(S^+\)\hyperref[SE]{(Definition
3.1)},we define \(WS^+\) and find inequalities between \(WS^+\),\(WS\) and \(S\)
\end{remark}

\subsection{Definition of \(WS^+\)}

In this subsection, we define the objects and proove the results needed for the general theorem regarding templates for 
weak Schur numbers.

@@

\begin{definition}
Let \( (k,b) \in (\mathbb{N}^*)^2\). If there exist \(p\) such that exists a partition of \([\![1, p]\!]\) into \(k\)
subsets which is a \(b\)-WS-template of \(k\) colors and lenght \(p\), we note:
\\\\\(WS_b^+=-b+\max \{p\in \mathbb{N}^*\)/ there exists a partition of \([\![1, p]\!]\) into \(k\) subsets which is a
\(b\)-WSF-template of \(k\) colors and lenght \(p\) \}
\\\\
If this \(p\) does not exist, we set \(WS_b^+= 0\)
\end{definition}

\begin{definition}
Let \( n \in \mathbb{N}^*\), we define \(WS^+(n)\)=\(\max_{b\in \mathbb{N}^*} \{WS_b^+(n)\}\)
\end{definition}

\begin{proposition}
	Let \(n \in [\![2, +\infty]\!]\), we have :
	\[
	\frac{3}{2}WS(n-1)+1 \leqslant WS^+(n) \leqslant WS(n)
	\]
\end{proposition}

@@

\begin{remark}
	\(WS^+\) and \(WS\) have the same asymptotic growth rate.
\end{remark}

@@

In particular, if we choose \(p = S(k)\) and \(q = WS^+(n)\) in the last theorem, the next corollary follows.

\begin{corollary}
\( \forall (n,k) \in (\mathbb{N}^*)^2 \text{, } let ~ b_{max}=max \{b\in \mathbb{N}^*/ WS_b^+(n+1) = WS^+(n+1)\},\) \[
WS(n+k) \geqslant S(k) WS^+(n+1)+b_{max}\]
\end{corollary}

\begin{remark}
In the SF-template construction for Schur numbers, the additive constant comes from the fact that the special color does 
not necessarily appear right at the begining of the repeating pattern. Likewise, \(b_max\) can actually be replaced by \\
\[\max \left\{ b + \min (A_{n+1} \backslash [\![1, b ]\!]) - 1~|~ WS_b^+(n+1) = WS^+(n+1) \right\}\]
\end{remark}

@@

\begin{proposition}
Let \((b, k, p) \in \mathbb{N}^*)^3\) and let \(f\) be a colouring associated to a b-WSF-template of length \(p\) with \(k\) colors. Let 
\(c \in \mathbb{N}\) (\(c = \min (A_{k+1} \backslash [\![1, b ]\!]) - 1\) works) and assume there there exists a colouring \(g\) of 
\([\![b + 1, b + c]\!]\) with \(k\) colors such that:
\begin{itemize}
	\item \(\forall c \in [\![1, k]\!], \forall (x, y) \in  [\![1, a + b]\!] \times  [\![b + 1, a + b]\!], (f(x) = f(y) \text{ and } \pi(x + y) \leqslant b + c) 
	\implies g(\pi(x + y)) \neq f(x)\)
	\item \(\forall c \in [\![1, k]\!], \forall (x, y) \in  [\![1, a + b]\!] \times  [\![b + 1, b + c]\!],  (f(x) = g(y) \text{ and } \pi(x + y) \leqslant b + c) 
\implies g(\pi(x + y)) \neq f(x)\)
\end{itemize}
Then, for every \(n \in \mathbb{N}^*\), by using on the last row the colouring \(i \longmapsto g(i - p S(n)\), we have\\
\[ WS(n+k) \geqslant WS^+(k+1) S(n) + b + c\]
\end{proposition}

@@

We also have a similar theorem where only \(WS^+\) is involved.

@@

\begin{corollary}
	Let \(n, k \in \mathbb{N}^*\), we have \\
	\[ WS^+(n+k) \geqslant S^+(k+1)WS^+(n) \]
\end{corollary}

@@

\[
4S(n) + 1 \leqslant WS(n+1)
\]
\[
13S(n) + 8 \leqslant WS(n+2)
\]
\[
42S(n) + 24 \leqslant WS(n+3)
\]
\[
132S(n) + 26 \leqslant WS(n+4)
\]

The first two inequalities were found by Rowley, they are detailed in [2]. The third inequality is optimal and was found with a SAT solver. 
It uses the first sophistication explained in the previous subsection in order to add the last number in the first color.  
As for the fourth inequality, it was obtained by combining an optimal SF-template of length 33 with a WSF-template of length 4. 
The best template we could get with a computer search gives the inequality \(WS(n+4) \geqslant 127 S(n) + 68\). 
It was also found with the SAT solver. In order to reduce the search space, we only looked for WSF-templates of 
5 colors which start with a good \(WS(4)\) partition. However, this approach most likely prevents us from finding the best WSF-templates 
as we explain in the next subsection for weakly sum-free partitions. We highly suspect that there exists more efficient WSF-templates 
with \(n \geqslant 5\) colors. One may try to go over a different search space using a Monte-Carlo method, as in \cite{Bouzy2015AnAP}. 
This could be the suject of a future work. Further details about the encoding as a SAT problem can be found in the
\hyperref[SAT]{SAT section}. \\

@@

With \( S(9) \geqslant 17803 \), we found a new lower bound for \(WS(10)\) using Rowley's inequality. 
Moreover, the third inequality gives new lower bounds for \(WS(9)\) and \(WS(14)\).

>>>>

In this section, we generalize Rowley's constructions in \cite{RowleyWS}. We then introduce, by analogy with the third
section, the
integer \(\WS^+(n)\)
to build suitable templates.

@@

Up to now, there was no equivalent for weak Schur numbers of Abott and Hanson's construction \cite{AbbottHanson}. Here
we
give a general lower bound for weak Schur numbers as a function of both regular and weak Schur numbers.
The following theorem, inspired by Rowley's inequalities for \(\WS (n+1)\) and \(\WS (n+2)\), was found and proved
by Romain Ageron.

@@

In particular, if we choose \(q = \WS (n)\) and \(p = S(k)\) in the last theorem, the next corollary follows.

\begin{corollary}
\( \forall (n,k) \in (\mathbb{N}^*)^2 \text{, } \WS (n+k) \geqslant S(k) \left (\WS (n) + \left \lceil \frac{\WS (n)}{2}
\right \rceil +1 \right) + \WS (n)\)
\end{corollary}

@@

\begin{remark}
In the above ineqality, a "\(+1\)" can be added to the lower bound if \(\WS (n)\) is odd (more generally if \(q\) is odd in the theorem). However, it makes the proof less
clear and it is never useful in practice.
\end{remark}

@@

\begin{remark}
This formula includes the results of Rowley \cite{RowleyWS} as a special case. For \(n>2\),
this formula does not give new lower bounds but in the same way as we introduced \(S^+\)\hyperref[SE]{(Definition
3.1)},we define \(\WS^+\) and find inequalities between \(\WS^+\),\(\WS\) and \(S\)
\end{remark}

\subsection{Definition of \(\WS^+\)}

In this subsection, we define the objects and prove the results needed for the general theorem regarding templates for
weak Schur numbers.

@@

\begin{definition}
Let \( (k,b) \in (\mathbb{N}^*)^2\). If there exist \(p\) such that exists a partition of \([\![1, p]\!]\) into \(k\)
subsets which is a \(b\)-WSF-template of \(k\) colors and lenght \(p\), we note:
\\\\\(\WS_b^+=-b+\max \{p\in \mathbb{N}^*\)/ there exists a partition of \([\![1, p]\!]\) into \(k\) subsets which is a
\(b\)-WSF-template of \(k\) colors and lenght \(p\) \}
\\\\
If this \(p\) does not exist, we set \(\WS_b^+= 0\)
\end{definition}

\begin{definition}
Let \( n \in \mathbb{N}^*\), we define \(\WS^+(n)\)=\(\max_{b\in \mathbb{N}^*} \{\WS_b^+(n)\}\)
\end{definition}

\begin{proposition}
	Let \(n \in [\![2, +\infty]\!]\), we have :
	\[
	\frac{3}{2} \WS (n-1)+1 \leqslant \WS^+(n) \leqslant \WS (n)
	\]
\end{proposition}

@@

\begin{remark}
	\(\WS^+\) and \(\WS\) have the same asymptotic growth rate.
\end{remark}

@@

In particular, if we choose \(p = S(k)\) and \(q = \WS^+(n)\) in the last theorem, the next corollary follows.

\begin{corollary}
\( \forall (n,k) \in (\mathbb{N}^*)^2 \text{, } let ~ b_{max}=max \{b\in \mathbb{N}^*/ \WS_b^+(n+1) = \WS^+(n+1)\},\) \[
\WS(n+k) \geqslant S(k) \WS^+(n+1)+b_{max}\]
\end{corollary}

\begin{remark}
In the SF-template construction for Schur numbers, the additive constant comes from the fact that the special color does
not necessarily appear right at the begining of the repeating pattern. Likewise, \(b_max\) can actually be replaced by \\
\[\max \left\{ b + \min (A_{n+1} \backslash [\![1, b ]\!]) - 1~|~ \WS_b^+(n+1) = \WS^+(n+1) \right\}\]
\end{remark}

@@

\begin{proposition}
Let \((b, k, p) \in \mathbb{N}^*)^3\) and let \(f\) be a colouring associated to a b-WSF-template of length \(p\) with \(k\) colors. Let
\(c \in \mathbb{N}\) (\(c = \min (A_{k+1} \backslash [\![1, b ]\!]) - 1\) works) and assume there there exists a colouring \(g\) of
\([\![b + 1, b + c]\!]\) with \(k\) colors such that:
\begin{itemize}
	\item \(\forall c \in [\![1, k]\!], \forall (x, y) \in  [\![1, a + b]\!] \times  [\![b + 1, a + b]\!], (f(x) = f(y) \text{ and } \pi(x + y) \leqslant b + c)
	\implies g(\pi(x + y)) \neq f(x)\)
	\item \(\forall c \in [\![1, k]\!], \forall (x, y) \in  [\![1, a + b]\!] \times  [\![b + 1, b + c]\!],  (f(x) = g(y) \text{ and } \pi(x + y) \leqslant b + c)
\implies g(\pi(x + y)) \neq f(x)\)
\end{itemize}
Then, for every \(n \in \mathbb{N}^*\), by using on the last row the colouring \(i \longmapsto g(i - p S(n)\), we have\\
\[ \WS(n+k) \geqslant \WS^+(k+1) S(n) + b + c\]
\end{proposition}

@@

We also have a similar theorem where only \(\WS^+\) is involved.

@@

\begin{corollary}
	Let \(n, k \in \mathbb{N}^*\), we have \\
	\[ \WS^+(n+k) \geqslant S^+(k+1) \WS^+(n) \]
\end{corollary}

@@

\[
\WS(n+1) \geqslant 4S(n) + 1 
\]
\[
\WS(n+2) \geqslant 13S(n) + 8
\]
\[
\WS(n+3) \geqslant 42S(n) + 24
\]
\[
\WS(n+4) \geqslant 132S(n) + 26
\]

The first two inequalities were found by Rowley, they are detailed in [2]. The third inequality is optimal and was found with a SAT solver.
It uses the first sophistication explained in the previous subsection in order to add the last number in the first color.
As for the fourth inequality, it was obtained by combining an optimal SF-template of length 33 with a WSF-template of length 4.
The best template we could get with a computer search gives the inequality \(\WS(n+4) \geqslant 127 S(n) + 68\).
It was also found with the SAT solver. In order to reduce the search space, we only looked for WSF-templates of
5 colors which start with a good \(\WS(4)\) partition. However, this approach most likely prevents us from finding the best WSF-templates
as we explain in the next subsection for weakly sum-free partitions. We highly suspect that there exists more efficient WSF-templates
with \(n \geqslant 5\) colors. One may try to go over a different search space using a Monte-Carlo method, as in \cite{Bouzy2015AnAP}.
This could be the suject of a future work. Further details about the encoding as a SAT problem can be found in the
\hyperref[SAT]{SAT section}. \\

@@

With \( S(9) \geqslant 17803 \), we found a new lower bound for \(\WS(10)\) using Rowley's inequality.
Moreover, the third inequality gives new lower bounds for \(\WS(9)\) and \(WS(14)\).
